PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2022-01-11 main.tex
Add discussion of figure 8

\begin{table}
\caption{Summary of Full Disk Simulations Run}
\begin{tabular}{llllll} \hline \hline
Name    & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\alpha^{d}$ &  \\ \hline
fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &   \\
fdHiShallow    & $5 \times 10^{22}$ & 903,687 & 100                                                        & 0.5                              &   \\
fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &   \\
fdLo                & $1 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &   \\ \hline
\end{tabular}
\begin{flushleft}
\textsc{Note} \\ {$^a$ Planetesimal mass [g] \\
		       $^b$ Number of planetesimals \\
		       $^c$ Solid surface density normalization (relative to MMSN) \\
		       $^d$ Solid surface density power law index } \\
\end{flushleft}
\label{tab:sims}
\end{table}

@@

@@

@@

How to reconcile our concerns with the results of \citet{wallace17}?

>>>>

\begin{table}
% I'm going to replace the fdLo simulation with a lower resolution version m_pl = 5e22 for consistency
% Originally wanted to run everything at m_pl = 1e22, which corresponds to 100km bodies, but this wasn't feasible at higher Sigma
\caption{Summary of Full Disk Simulations Run}
\begin{tabular}{llllll} \hline \hline
Name    & $m_{pl}^{a}$ & $N_{pl}^{b}$ & $A^{c}$ & $\alpha^{d}$ &  \\ \hline
fdHi                 & $5 \times 10^{22}$ & 903,687 & 100                                                         & 1.5                              &   \\
fdHiShallow    & $5 \times 10^{22}$ & 903,687 & 100                                                        & 0.5                              &   \\
fdHiSteep       & $5 \times 10^{22}$ & 903,687 & 100                                                         & 2.5                              &   \\
fdLo                & $1 \times 10^{22}$ & 45,185    & 1                                                             & 1.5                              &   \\ \hline
\end{tabular}
\begin{flushleft}
\textsc{Note} \\ {$^a$ Planetesimal mass [g] \\
		       $^b$ Number of planetesimals \\
		       $^c$ Solid surface density normalization (relative to MMSN) \\
		       $^d$ Solid surface density power law index } \\
\end{flushleft}
\label{tab:sims}
\end{table}

@@

% Another important point: the accretion boundary doesn't move as we change surface density (how does t_relax and t_coll scale with sigma?). More evidence that it just depends on alpha(r)

@@

Next, we compare the effect of varying the initial solid surface density profile on the resulting planetesimal and embryo distribution. The final orbital period-eccentricity state of the particles is shown in figure \ref{fig:surfden_profiles}, with point sizes indicating the relative masses of the bodies. There is a clear trend between solid surface density at a given orbital period and the eccentricities of the remaining planetesimals. This trend is largely set by the initial conditions, as the gravitational stirring is more vigorous when bodies are packed together closely and higher eccentricities are required to produce an equilibrating aerodynamic drag force (see equations \ref{eq:eq:vs_timescale} and \ref{eq:ts_stokes}). Despite having significantly different masses, the planetary embryos formed in each case have remarkably similar eccentricities. This is likely due to the fact that inelastic collisions play a more significant role where the solid surface density is highest, which offsets the fact that the initial bodies started off in a dynamically hotter state.

@@

How to reconcile our concerns with the results of \citet{wallace17}? Show inner disk test with different collision models. Bounce/merge model delays onset of runaway growth, with smaller planetesimals being delayed by longer. Does not affect eccentricity or mass of resulting embryos. Because $v_{esc}$ grows with mass, a more realistic collision model only delays the onset of runaway growth.
